Interactive Summarization of Relational Tables

### 2014-10-29 TableSummarization/Paper/TableSummarization.tex
Changes to writeup

The total score for our list of rules is given by $$\text{Score}(R) = \sum_{r \in R} MCount(r)W(r)$$. Our problem is to choose the rule-list that maximises total score. We use $MCount$ rather than Count to increase coverage of the table. If we had defined total score as $$\sum_{r \in R} \text{Count}(r)W(r)$$, then our optimal rule-list would contain 
%TODO: Finish writing this part.

>>>>

The total score for our list of rules is given by $$\text{Score}(R) = \sum_{r \in R} MCount(r)W(r)$$. Our problem is to choose the rule-list that maximises total score. We use $MCount$ rather than Count to increase coverage of the table. If we had defined total score as $$\sum_{r \in R} \text{Count}(r)W(r)$$, then our optimal rule-list would contain rules that repeatedly refer to the most `summarizable' part of the table. For instance, if $a$ and $b$ were the most common values in columns $A$ and $B$, then the summary could consist of rules $(a, b, \star)$, $(a, \star, \star)$, and $(\star, b, \star)$, which tells us nothing about the part of the table with values other than $a$ and $b$.
%TODO: Write an actual example? To also verify what actually happens.
